Comparison of long and short amplicon metabarcoding for determination of fungal species diversity and spatial turnover in an ectomycorrhizal West African woodland

### 2019-08-12 writing/MSA2019_presentation.Rnw
add author affiliations

\title{Turnover scale of soil fungal community composition}
\subtitle{Presentation for Anna's Group Meeting}
\author{Brendan Furneaux}
\date{26 April, 2019}

@@

>>>>

\title{Comparison of long and short amplicon metabarcoding for determination of fungal species diversity and spatial turnover in an ectomycorrhizal West African woodland}
\author{\mbox{\textbf{Brendan Furneaux}\inst{1}} \and \mbox{Mohammad Bahram\inst{2}} \and \mbox{Nourou Yorou\inst{3}} \and \mbox{Anna Rosling\inst{1}} \and \mbox{Martin Ryberg\inst{1}}}
\institute{\inst{1}Uppsala University \and \inst{2}Swedish University of Agricultural Sciences \and \inst{3}University of Parakou}
\date{13 August, 2019}

@@

% # Metabarcoding
% 
%   - Cloning + Sanger -> 454 -> Illumina
%   - For fungi, usually ITS2
%       - short
%       - intraspecific variation in most groups
%       - good database support (Unite 8.0 - 817 130 fungal sequences)
%       - ITS is "official barcode for fungi" \cite{schoch2012}
%       - fungal specific primers
%   - problems
%       - not alignable
%       - cannot place unknown sequences
%       - variant 5.8S
%       - variable length
%   
%   - LSU (26S/28S)
%       - alternating highly conserved domains and variable regions
%       - widely used for phylogenies
%       - universal primers
%       - less variable length
%       - more conserved than ITS
%       - not as good database support (RDP 11 fungal LSU - 125 525, Silva 132 LSU 907 382 of which )
%   - SSU (18S)
%       - alternating highly conserved and variable regions
%       - more conserved than LSU
%       - used for barcoding prokaryotes and "protists"
%       - good database support (Silva SSU), but not as good for fungi
